### 2013-04-19 Rctl/inst/doc/manual.Rnw
[Manual] Minor updates
Add Sweave.sty and minor updates to the manual
Fixing issue #13, the D/test/data files are now used in the manual also

\begin{tabular}{lrrrrr}
      & Marker1 & Marker2 & Marker3 & ... & MarkerN \\
Ind1  & 1 & 1 & 1 & ... & 2 \\
Ind2  & 1 & 2 & 2 & ... & 1 \\
Ind3  & 2 & 2 & 1 & ... & 1 \\
...   & ... & ... & ... & ... & ... \\
IndN  & 1 & 1 & 1 & ... & 2 \\
\end{tabular}

@@

\begin{tabular}{lrrrrr}
      & Trait1 & Trait2 & Trait3 & ... & TraitN \\
Ind1  & 5.8    & 11.0   & 9.0    & ... & 1.6 \\
Ind2  & 6.3    & 12.2   & NA     & ... & 1.3 \\
Ind3  & 5.1    & 11.1   & 12.3   & ... & 2.0 \\
...   & ...    & ...    & ...    & ... & ... \\
IndN  & 9.8    & 15.8   & 23.0   & ... & 3.4 \\
\end{tabular}

After verifying your files are formatted correctly (this is the source of most errors).
Start R and load in the data, check that the output looks like below:
<<echo=TRUE,eval=FALSE>>=
setwd("<PATH_TO_DATA>")
genotypes <- read.csv("genotypes.csv",row.names=1,col.names=TRUE)
traits <- read.csv("traits.csv",row.names=1,col.names=TRUE)
genotypes[1:5,1:10]    #Show the first 5 individuals, 10 markers
traits[1:5,1:10]       #Show the first 5 individuals, 10 traits
@

@@

@@

\bigskip
\textbf{\sffamily Significance using CTLpermute}
\nopagebreak

Explains how to determine CTL significance using the CTLpermute function.

@@

\newpage
{\small
\noindent \textbf{\sffamily Package CTL function overview} \\
\noindent \begin{tabular}{ll} 
\hspace*{25mm} & \hspace*{103mm} \\ \hline
CTLscan & Main function for Genome wide scan for Correlated Trait Loci \\
CTLscan.network & Scan only a subset of traits for CTL using start gene(s) \\
CTLpermute & Significance thresholds for CTL by permutation\\
plot & Plot CTL profiles at increasing cut-offs \\
image & Image a multiple phenotype scan \\
\hline
\end{tabular}
}

>>>>

\begin{tabular}{lrrrrr}
     & Chromosome & Location & Ind1 & Ind2 & Ind3 & ... & IndN \\
Marker1  & 1 & 0.0 & 1 & 1 & 1 & ... & 2 \\
marker2  & 1 & 5.3 & 1 & 2 & 2 & ... & 1 \\
marker3  & 1 & 7.8 & 2 & 2 & 1 & ... & 1 \\
...   & ... & ... & ... & ... & ... & ... & ... \\
MarkerN  & 7 & 120.1 & 1 & 1 & 1 & ... & 2 \\
\end{tabular}

@@

\begin{tabular}{lrrrrr}
      & Chromosome & Location & Ind1 & Ind2 & Ind3 & ... & IndN \\
Trait1  & ... & ... & 5.8    & 11.0   & 9.0    & ... & 1.6 \\
Trait2  & ... & ... & 6.3    & 12.2   & NA     & ... & 1.3 \\
Trait3  & ... & ... & 5.1    & 11.1   & 12.3   & ... & 2.0 \\
...   & ... & ... & ...    & ...    & ...    & ... & ... \\
Trait  & ... & ... & 9.8    & 15.8   & 23.0   & ... & 3.4 \\
\end{tabular}

After verifying your files are formatted correctly (this is the source of most errors).
Start R and load in the data, check that the output looks like below:
<<echo=TRUE,eval=FALSE>>=
  setwd("/Path/To/Data/")
  genotypes <- read.csv("genotypes.csv",row.names=1, header=FALSE,sep="\t")
  traits <- read.csv("phenotypes.csv",row.names=1, header=FALSE,sep="\t")
  genotypes[1:5,1:10]    #Show 5 individuals, 8 markers, and genetic locations
  traits[1:5,1:10]       #Show 5 individuals, 8 traits, and genetic locations
  mapinfo <- genotypes[,1:2]
  genotypes <- genotypes[,-c(1,2)]  # Remove the genetic locations
  traits <- traits[,-c(1,2)]        # Remove the genetic locations
@

@@

\bigskip
\textbf{\sffamily Get a list of significant CTLs}
\nopagebreak

Get significant CTL interactions by using CTLsignificant.

<<echo=TRUE,eval=FALSE>>=
sign <- CTLsignificant(ctl_scan)
@

@@

@@

\bigskip
{\small
\noindent \textbf{\sffamily Package CTL function overview} \\
\noindent \begin{tabular}{ll} 
\hspace*{25mm} & \hspace*{103mm} \\ \hline
CTLscan & Main function for Genome wide scan for Correlated Trait Loci \\
CTLscan.network & Scan only a subset of traits for CTL using start gene(s) \\
CTLpermute & Significance thresholds for CTL by permutation\\
plot & Plot CTL profiles at increasing cut-offs \\
image & Image a multiple phenotype scan \\
\hline
\end{tabular}
}
